Parameterless Population Pyramid

### 2013-09-17 Parameterless Population Pyramid/main.tex
Added a diagram, more citation updates

\section{The P3 Algorithm}
TODO Overview.  Use graphic.

@@

\subsection{Crossover}
TODO Explain how entropy becomes clusters efficiently $O(n^2)$, cluster ordering,
keep changes that don't reduce fitness, removal of zero entropy sub-clusters,
keep donating until a change is made.

@@

\subsection{Randomly Generated Problem Classes}
TODO Nearest Neighbor NK with wrapping neighborhoods, Ising Spin Glasses on toroidal
grids with only -1, 1 spins, Maximum Satisfiability constructed with known global
optimum.

@@

>>>>

TODO Talk about ALPS~\cite{hornby:2006:alps}.

\section{The P3 Algorithm}
TODO Overview.  Use Figure~\ref{fig-p3}.

\begin{figure}
  \centering
  \includegraphicsfit{P3_big_fail}
  \caption{Example}
  \label{fig-p3}
\end{figure}

@@

\subsection{Crossover}
TODO Explain how entropy becomes clusters efficiently $O(n^2)$~\cite{gronau:2007:upgma}, cluster ordering,
keep changes that don't reduce fitness, removal of zero entropy sub-clusters,
keep donating until a change is made.

@@

\subsection{Randomly Generated Problem Classes}
TODO Nearest Neighbor NK with wrapping neighborhoods, Ising Spin Glasses on toroidal
grids with only -1, 1 spins~\cite{saul:1994:spinglass}.
Used\footnote{\url{http://www.informatik.uni-koeln.de/spinglass/}}, Maximum Satisfiability constructed with known global
optimum.

@@

TODO Mention 1.5 trillion evaluations and 150,000 runs (average 10 million evaluations per run).
